### 2016-09-13 text/formal_background.tex
Do more on transitivity edges.

\begin{definition}{Transitive Closure\\}
\label{def:instance_closure}
Let $g$ be a graph $\langle V,E,(s, t),\tau\rangle \in \textsc{TG}$. Then the transitive closure $g^{*} = \langle V,E',(s', t'),\tau', \VT, \ET' \rangle \in \textsc{TG}$ is created by $E' = E \cup E_{tc}$.

The new edges $e_{tc} \in E_{tc}$ are created such that:

\begin{itemize}
\item $v_1\xrightarrow{e_{tc}}v_2 | \exists v_1\xrightarrow{e_i}v_i, v_i\xrightarrow{e_j}v_j, \dots, v_k\xrightarrow{e_k}v_2$
\item $s'(e_{tc}) = v_1$, $t'(e_{tc}) = v_2$
\item $\tau(e_{tc}) = $
\end{itemize}

@@

Given a graph, its transitive closure includes, besides the original graph, all the edges belonging to the transitive closure of indirect links in that graph. Note that these transitive edges are identified by the function $\mathit{isIndirect}$.

@@

\begin{itemize}
\item Backward links injectively match from contract into PC onto traceability links. Source and target of backward links on contract must match the source and target of the traceability link of the PC.
\end{itemize}

We must also define a function to match link structures, such as backward links and the traceability links (to be discussed).

\begin{definition}{Link Homomorphism\\}
\label{def:link_homomorphism}
Consider two sets of links $L = \{E_{L}, (s_{L}, t_{L})\}$, and $T = \{E_{T}, (s_{T}, t_{T})\}$. Note that these could be backward links or traceability links.

We define an injective homomorphism function $f$ to match $L$ over $T$, such that:

\begin{itemize}
\item $\forall e_L \in E_L:$
\begin{itemize}
\item $\forall e_T \in E_T | f(e_L) = e(T)$
\end{itemize}
\end{itemize} 
\end{definition}

@@

For example, we may need to find a homomorphism between two structures $S_1 = \langle A, B, L\rangle$ and  $S_2 = \langle A', B', L'\rangle$, where $A, A', B, B' \in TG$ and $L, L'$ are links of the form $\{E, (s, t)\}$.

This overall homomorphism will compose the homomorphism $f(A) = A'$, $g(B) = B'$, $h(L) = L'$, where f and g are the homomorphisms to be found, and h is the link homomorphism.

A reviewer pointed out that we also require that these sub-homomorphisms are consistent with each other. That is, the link homomorphism h must agree with 
the bindings given by f and g.

\bentley{Complete this}

>>>>

\begin{definition}{Transitive Closure\\}
\label{def:instance_closure}
Let $g$ be a graph $\langle V,E,(s, t),\tau\rangle \in \textsc{TG}$. Then the transitive closure $g^{*} = \langle V,E',(s', t'),\tau', \VT, \ET' \rangle \in \textsc{TG}$ is created such that:

\begin{itemize}
\item $E' = E \cup E_{tc}$ where each new edge $e_{tc} \in E_{tc}$ is created between vertices $v_1$ and $v_2$ in $V$:
\begin{itemize}
\item $v_1\xrightarrow{e_{tc}}v_2 | \exists v_1\xrightarrow{e_i}v_i, v_i\xrightarrow{e_j}v_j, \dots, v_k\xrightarrow{e_k}v_2$
\end{itemize}

\item $s'(e_{tc}) = v_1$, $t'(e_{tc}) = v_2$
\item $\tau(e_{tc}) = \mathit{indirect}$
\end{itemize}

@@

Given a graph, its transitive closure includes, besides the original graph, all the edges belonging to the transitive closure of indirect links in that graph. Note that these transitive edges are given a special type \textit{indirect}, and will be identified by the function $\mathit{isIndirect}$.

@@

For convenience, we also define a function to match components in our structures which contains only links. An example would be the backward link construct for DSLTrans rules, as discussed in Section~\ref{subsec:dsltrans_formal_structures}.

\begin{definition}{Link Homomorphism\\}
\label{def:link_homomorphism}
Consider two sets of links $A = \{E_{A}, (s_{A}, t_{A})\}$, and $B = \{E_{B}, (s_{B}, t_{B})\}$. Note that these could be backward links or traceability links.

We define a (trivial) injective homomorphism function $f$ to match $A$ over $B$, such that:

\begin{itemize}
\item $\forall e_A \in E_A:$
\begin{itemize}
\item $\exists e_b \in E_{B} | f(e_A) = e_b$
\item $f(s_{A}(e_A)) = s_{B}(e_B)$
\item $f(t_{A}(e_A)) = t_{B}(e_B)$
\end{itemize}
\end{itemize} 
\end{definition}

@@

For example, we may need to find a homomorphism $m$ between two structures $S_1 = \langle A, B, L\rangle$ and  $S_2 = \langle A', B', L'\rangle$, where $A, A', B, B' \in TG$ and $L, L'$ are links of the form $\{E, (s, t)\}$.

This overall homomorphism be composed of the sub-homomorphisms $f(A) = A'$, $g(B) = B'$, $h(L) = L'$, where $f$ and $g$ are the homomorphisms to be found, and $h$ is the link homomorphism. Note that $f$ and $g$ may have differing properties, such as being injective or not, motivating our consideration of three sub-morphisms.

Our definitions for these structures require that the components (such as $A$, $B$, and $L$) are all disjoint. Thus we consider the homomorphism to be trivially composed: $m = f \cup g \cup h$.

However, a reviewer pointed out that we also require that these sub-homomorphisms are consistent with each other. Namely that the link homomorphism $h$ must agree with the bindings given by $f$ and $g$. That is:

\bentley{Finish}
